Digital History in Finland, 1488-1828

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

>>>>

```
---

### DONE Kungliga subject topics (NEW!!)

Kyrkohistoria; Biblisk arkeologi;Exegetik;Homiletik;Dogmatik;Teologi; Praktisk Teologi; Teologisk etik

```{r ktopic1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Kyrkohistoria", "biblisk arkeologi", "Exegetik", "Homiletik", "Dogmatik", "Teologi", "Praktisk Teologi", "Teologisk etik"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)

rm(pics)
```

Idé- och lärdomshistoria;Antiken;Historia;Militärhistoria;

```{r ktopic2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)

rm(pics)
```

Filosofi;Metafysik;Logik

```{r ktopic3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Filosofi", "Metafysik", "Logik"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

4. Naturvetenskap;Matematik;Matematiska tabeller; Kemi;Astronomi;Geografi;Geologi;Meteorologi

```{r ktopic4, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Naturvetenskap", "Matematik", "Matematiska tabeller", "Kemi", "Astronomi", "Geografi", "Geologi", "Meteorologi"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

5. Retorik

```{r ktopic5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Retorik"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

6. Hebreiska språket; Grekiska språket;Latin

```{r ktopic6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Hebreiska språket", "Grekiska språket", "Latin"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

7. Politisk filosofi;Ekonomiska förhållanden; Nationalekonomi;Lantbruksekonomi;Ekonomi;Penningväsen;Penningvärde;Kreditväsen;Penningförfalskning;Moral;Pedagogik;Uppfsotringsverket;Uppfostran;Barnuppfostran;Jordbruk;Jordbrukslära;Jordbrukspolitik;Fiske

```{r ktopic7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Politisk filosofi","Ekonomiska förhållanden"," Nationalekonomi","Lantbruksekonomi","Ekonomi","Penningväsen","Penningvärde","Kreditväsen","Penningförfalskning","Moral","Pedagogik","Uppfsotringsverket","Uppfostran","Barnuppfostran","Jordbruk","Jordbrukslära","Jordbrukspolitik","Fiske"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

8. Biologi;Medicinalverket;Medicin;Veterinärmedicin;Medicinalväsen;Medicinalväxkter;Sjukdomar;Djursjukdomar;Djur;Husdjur;Djurskydd;Hästar;Hästkreatur;Hästkörning;Hästavel

```{r ktopic8, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Biologi","Medicinalverket","Medicin","Veterinärmedicin","Medicinalväsen","Medicinalväxkter","Sjukdomar","Djursjukdomar","Djur","Husdjur","Djurskydd","Hästar","Hästkreatur","Hästkörning","Hästavel"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

9. Kvinnor;Kvinnliga textilarbetare;Gravida kvinnor;Adelskvinnor;Kvinnorollen;Ensamstående kvinnor

```{r ktopic9, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Kvinnor","Kvinnliga textilarbetare","Gravida kvinnor","Adelskvinnor","Kvinnorollen","Ensamstående kvinnor"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

10. Högmålsbrott;Skattebrott;Brott;Brottslingar;Äktenskapsbrott;Våldsbrott;Trafikbrott;Gäldenärsbrott;Sabbattsbrott;Sexualbrott;Fridsbrott;Ekonomisk brottslighet;Religionsbrott;Juridik;Straff;Dödsstraff;Kroppsstraff;Straffarbete;Straffarbete;Fängelsestraff

```{r ktopic10, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}

catalogue <- "Kungliga"
years <- c(1640, 1828)
sel =  tolower(c("Högmålsbrott","Skattebrott","Brott","Brottslingar","Äktenskapsbrott","Våldsbrott","Trafikbrott","Gäldenärsbrott","Sabbattsbrott","Sexualbrott","Fridsbrott","Ekonomisk brottslighet","Religionsbrott","Juridik","Straff","Dödsstraff","Kroppsstraff","Straffarbete","Straffarbete","Fängelsestraff"))
places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")

df <- df0 %>% filter(catalog == catalogue)%>%
  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
  filter(publication_place %in% places)

lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# Selected catalogue and place with selected topics
pics <- list()
for (place in places) {

  df <- subset(dfl, publication_place == place)

  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
  df <- df %>% filter(hit)
  df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(place) +
       xlim(c(years[[1]], years[[2]]))
  pics[[place]] <- p

}

grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```
---
